---
title: "Distribuição t de Student"
author: "Prof. Omar"
output: pdf_document
---

```{r setup , include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      size = "footnotesize",
                      comment = NA,
                      warning = FALSE,
                      message = FALSE,
                      #out.width = "1\\linewidth",
                      fig.align = "center",
                      fig.width = 8, 
                      fig.height = 4, 
                      fig.show = "hold",
                      fig.path = "FigurasT/",
                      fig.pos = "!htb",
                      fig.cap = TRUE,
                      background = "#E6E6FA",
                      #background = "black",
                      dev = c("png",'pdf'),
                      res=300,
                      dpi = 300,
                      cache = TRUE)
```

```{r library, echo=FALSE,results='hide'}
library(tidyverse)
#library(tinytex)
library(knitr)
library(kableExtra)
library(xtable)
```


```{r echo=FALSE, fig.height=1, fig.width=4.5, fig.cap= ""}
ggplot(data.frame(x = c(-3, 3)), aes(x)) +
  stat_function(fun = dnorm,
                geom = "line",
                xlim = c(-3, 3)) +
  stat_function(fun = dnorm,
                geom = "area",
                fill = "gray",
                xlim = c(-3, 1)) +
  geom_segment(aes(x = 1, y = 0, 
                   xend = 1, yend = dnorm(1)),
               size = 0.5) +
   theme_void() +
  annotate("text",label=  bquote(t['(g.l.,' ~1-alpha/2 *')'])  
             ,x=0.82,y=0.0,
           hjust=-0.3,vjust=0.4,
           size = 3) +
  annotate("text",label="t",x=3,y=0.0,
           hjust=-0.3,vjust=0.3,
           size = 5) +
  annotate("text",label=bquote('P(t<'~ t['(g.l.,' ~1-alpha/2 *')'] *')'),x=-1,y=0.18,hjust=0,vjust=0.5,
           size = 5)
```


<!-- \begin{center} -->
<!-- Os valores tabelados correspondem aos pontos $x$ tais que $P(t_{g.l.} \leq x)$ -->
<!-- \end{center} -->

```{r, echo=FALSE,results='hide'}
options(digits = 4)
z1 <- seq(0,3.99,0.01)
qq <- round(pnorm(z1),4)
round(qq[1],4)

af1 <- c(0.900,0.950,0.975,0.995)
gl1 <- c(1:30,40,60,120,20000)
tt1 <- data.frame(gl=rep(gl1,each=length(af1)),
                 af=rep(af1,length(gl1))
                 )
tt <- round(qt(tt1$af,tt1$gl),3)
```



| g.l.   |   0.900   |   0.950   |   0.975   |   0.995   |
|-----|:--------:|:--------:|:--------:|:--------:|
| 1 |  `r tt[1]` |  `r tt[2]` |  `r tt[3]` | `r tt[4]` |
| 2 |  `r tt[5]`  |  `r tt[6]`  |  `r tt[7]`  |  `r tt[8]`  
| 3 |  `r tt[9]`  |  `r tt[10]`  |  `r tt[11]`  |  `r tt[12]`
| 4 |  `r tt[13]`  |  `r tt[14]`  |  `r tt[15]`  |  `r tt[16]`
| 5 |  `r tt[17]`  |  `r tt[18]`  |  `r tt[19]`  |  `r tt[20]`
| 6 |  `r tt[21]`  |  `r tt[22]`  |  `r tt[23]`  |  `r tt[24]`
| 7 |  `r tt[25]`  |  `r tt[26]`  |  `r tt[27]`  |  `r tt[28]`
| 8 |  `r tt[29]`  |  `r tt[30]`  |  `r tt[31]`  |  `r tt[32]`
| 9 |  `r tt[33]`  |  `r tt[34]`  |  `r tt[35]`  |  `r tt[36]`
| 10 |  `r tt[37]`  |  `r tt[38]`  |  `r tt[39]`  |  `r tt[40]`
| 11 |  `r tt[41]`  |  `r tt[42]`  |  `r tt[43]`  |  `r tt[44]`
| 12 |  `r tt[45]`  |  `r tt[46]`  |  `r tt[47]`  |  `r tt[48]`
| 13 |  `r tt[49]`  |  `r tt[50]`  |  `r tt[51]`  |  `r tt[52]`
| 14 |  `r tt[53]`  |  `r tt[54]`  |  `r tt[55]`  |  `r tt[56]`
| 15 |  `r tt[57]`  |  `r tt[58]`  |  `r tt[59]`  |  `r tt[60]`
| 16 |  `r tt[61]`  |  `r tt[62]`  |  `r tt[63]`  |  `r tt[64]`
| 17 |  `r tt[65]`  |  `r tt[66]`  |  `r tt[67]`  |  `r tt[68]`
| 18 |  `r tt[69]`  |  `r tt[70]`  |  `r tt[71]`  |  `r tt[72]`
| 19 |  `r tt[73]`  |  `r tt[74]`  |  `r tt[75]`  |  `r tt[76]`
| 20 |  `r tt[77]`  |  `r tt[78]`  |  `r tt[79]`  |  `r tt[80]`
| 21 |  `r tt[81]`  |  `r tt[82]`  |  `r tt[83]`  |  `r tt[84]`
| 22 |  `r tt[85]`  |  `r tt[86]`  |  `r tt[87]`  |  `r tt[88]`
| 23 |  `r tt[89]`  |  `r tt[90]`  |  `r tt[91]`  |  `r tt[92]`
| 24 |  `r tt[93]`  |  `r tt[94]`  |  `r tt[95]`  |  `r tt[96]`
| 25 |  `r tt[97]`  |  `r tt[98]`  |  `r tt[99]`  |  `r tt[100]`
| 26 |  `r tt[101]`  |  `r tt[102]`  |  `r tt[103]`  |  `r tt[104]`
| 27 |  `r tt[105]`  |  `r tt[106]`  |  `r tt[107]`  |  `r tt[108]`
| 28 |  `r tt[109]`  |  `r tt[110]`  |  `r tt[111]`  |  `r tt[112]`
| 29 |  `r tt[113]`  |  `r tt[114]`  |  `r tt[115]`  |  `r tt[116]`
| 30 |  `r tt[117]`  |  `r tt[118]`  |  `r tt[119]`  |  `r tt[120]`
| 40 |  `r tt[121]`  |  `r tt[122]`  |  `r tt[123]`  |  `r tt[124]`
| 60 |  `r tt[125]`  |  `r tt[126]`  |  `r tt[127]`  |  `r tt[128]`
| 120 |  `r tt[129]`  |  `r tt[130]`  |  `r tt[131]`  |  `r tt[132]`
| $\infty$ |  `r tt[133]`  |  `r tt[134]`  |  `r tt[135]`  |  `r tt[136]`







